Scoring_questionnaires2021

### 2021-08-24 Questionnaires_scoring2021.Rmd
c

# 345_356
read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_AQ <- list.files(pattern = "*.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

@@

db_AQ4<- db_AQ3%>%
  # mutate(DIF = TAS_1 + TAS_3 + TAS_6 + TAS_7 + TAS_9 + TAS_13+ TAS_14)%>%
  # mutate(EOT = TAS_8+TAS_15+TAS_16+TAS_20+TAS_5+TAS_10+TAS_18+TAS_19)%>%
  # mutate(DDF = TAS_2+TAS_11+TAS_12+TAS_17+TAS_4)%>%
  mutate(SS = AQ_1+ AQ_11+ AQ_13 + AQ_15+ AQ_22 + AQ_36 + AQ_44 + AQ_45 + AQ_47 + AQ_48)%>%
  mutate(AS = AQ_2+ AQ_4 + AQ_10+AQ_16+AQ_25+AQ_32+AQ_34+AQ_37+AQ_43+AQ_46)%>%
  mutate(ATD = AQ_5+AQ_6+AQ_9+AQ_12+AQ_19+ AQ_23+AQ_28+AQ_29+AQ_30+AQ_49)%>%
  mutate(COM = AQ_7+AQ_17+AQ_18+AQ_26+AQ_27+AQ_31+AQ_33+AQ_35+AQ_38+AQ_39)%>%
  mutate(IMAG = AQ_3+AQ_8+AQ_14+AQ_20+AQ_21+ AQ_24+AQ_40+AQ_41+AQ_42+AQ_50)%>%
  # mutate(TAS_Total = DIF + DDF + EOT)%>%
  mutate(AQ = SS + AS +ATD + COM + IMAG)%>%
  select(c(completion_code, AQ))

@@

@@

View(db_TAS)

@@

db_TAS1<- db_TAS%>%
  select(c(16,33:71))

@@

db_TAS2
# note the gorilal tas labels have a zero, like 01 instead of 1
?recode
db_TAS3<- db_TAS2 %>%
  mutate_at(c('TAS_04', 'TAS_05', 'TAS_10', 'TAS_18', 'TAS_19'), 
            funs(car::recode(., "1=5; 2=4; 3=3; 4=2; 5 =1")))%>%
  mutate(DIF = TAS_01 + TAS_03 + TAS_06 + TAS_07 + TAS_09 + TAS_13+ TAS_14)%>%
  mutate(EOT = TAS_08+TAS_15+TAS_16+TAS_20+TAS_05+TAS_10+TAS_18+TAS_19)%>%
  mutate(DDF = TAS_02+TAS_11+TAS_12+TAS_17+TAS_04)%>%
  mutate(TAS = DIF + DDF + EOT)

@@

@@

colnames(db_DASS)
db_DASS1<- db_DASS%>%
  select(c(12,13,16,33:73))

@@

db_DASS4<- select(db_DASS3, c(1:2,29,25:28))

@@

@@

@@

db_BPQ2
db_BPQ3<- select(db_BPQ2, 1,2,29)
```

@@

@@

db_BVAQ3<- select(db_BVAQ1, c(1,2,43))
```

@@

db_vision <- list.files(pattern = "*-8nsp.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))
db_mhealth <- list.files(pattern = "*-v2gn.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

@@

bind (db_mhealth, db_vision, db_age, by = `Participant Private ID`)

colnames(db_age)
db_age$age_response_specific
db_age$gender_response
db_age$`gender_response-quantised`
# db_age$`AgeResponse-text`
db_age1<- select(db_age, c(1,13,16,36,37,41))

@@

@@

db_IQ1<- select(db_IQ, c(1,13,16, 37,45:48))

@@

colnames(db_IQ3)
db_IQ4<- select(db_IQ3,c(1,7,6))

@@

left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS, by = "completion_code")

@@

db_BPQ3

left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3, by = "completion_code")

db_self_rep<- Reduce(merge, list(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS))

@@

>>>>

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/AQ")
# 345_356
read_selfrep1 <- function(flnm) {
    read_excel(flnm) %>%
        mutate(filename = flnm)
}

db_AQ <- list.files(pattern = "*.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep1(.))

db_AQ <- read_excel("data_exp_11458-v9_questionnaire-7uqw-4489770.xlsx")

@@

db_AQ4<- db_AQ3 %>%
  # mutate(DIF = TAS_1 + TAS_3 + TAS_6 + TAS_7 + TAS_9 + TAS_13+ TAS_14)%>%
  # mutate(EOT = TAS_8+TAS_15+TAS_16+TAS_20+TAS_5+TAS_10+TAS_18+TAS_19)%>%
  # mutate(DDF = TAS_2+TAS_11+TAS_12+TAS_17+TAS_4)%>%
  mutate(SS = AQ_1+ AQ_11+ AQ_13 + AQ_15+ AQ_22 + AQ_36 + AQ_44 + AQ_45 + AQ_47 + AQ_48)%>%
  mutate(AS = AQ_2+ AQ_4 + AQ_10+AQ_16+AQ_25+AQ_32+AQ_34+AQ_37+AQ_43+AQ_46)%>%
  mutate(ATD = AQ_5+AQ_6+AQ_9+AQ_12+AQ_19+ AQ_23+AQ_28+AQ_29+AQ_30+AQ_49)%>%
  mutate(COM = AQ_7+AQ_17+AQ_18+AQ_26+AQ_27+AQ_31+AQ_33+AQ_35+AQ_38+AQ_39)%>%
  mutate(IMAG = AQ_3+AQ_8+AQ_14+AQ_20+AQ_21+ AQ_24+AQ_40+AQ_41+AQ_42+AQ_50)%>%
  # mutate(TAS_Total = DIF + DDF + EOT)%>%
  mutate(AQ = SS + AS +ATD + COM + IMAG)%>%
  select(c(completion_code, AQ))

@@

library(readxl)
db_TAS <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/TAS/data_exp_11458-v9_questionnaire-pdlt-4489770.xlsx")

@@

# View(db_TAS)

@@

db_TAS1<- db_TAS%>%
  select(c(16,32:71))

@@

colnames(db_TAS2)
# note the gorilal tas labels have a zero, like 01 instead of 1
?recode

db_TAS3<- db_TAS2 %>%
  mutate_at(c('TAS_04', 'TAS_05', 'TAS_10', 'TAS_18', 'TAS_19'), 
            funs(car::recode(., "1=5; 2=4; 3=3; 4=2; 5 =1")))%>%
  mutate(DIF = TAS_01 + TAS_03 + TAS_06 + TAS_07 + TAS_09 + TAS_13+ TAS_14)%>%
  mutate(EOT = TAS_08+TAS_15+TAS_16+TAS_20+TAS_05+TAS_10+TAS_18+TAS_19)%>%
  mutate(DDF = TAS_02+TAS_11+TAS_12+TAS_17+TAS_04)%>%
  mutate(TAS = DIF + DDF + EOT)

@@

library(readr)
db_DASS <- read_xlsx("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")

("Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")

@@

colnames(db_DASS)
db_DASS1<- db_DASS%>%
  select(c(12,13,16,32:74))

@@

db_DASS4<- select(db_DASS3, c(1:2,29,25:28))
db_DASS4

@@

library(readr)
db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/All_scores_IAS350_2021-08-23.csv")
db_IAS

@@

library(readxl)
# db_BPQ <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ/data_exp_11458-v9_questionnaire-bbc4-4489770.xlsx")

@@

db_BPQ2
db_BPQ3<- select(db_BPQ2, 1,2,29)
db_BPQ3
```

@@

library(readxl)
# db_BVAQ <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1/data_exp_11458-v9_questionnaire-83b1-4489770.xlsx")

@@

db_BVAQ3<- select(db_BVAQ1, c(1,2,43))

db_BVAQ3
```

@@

# db_age <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-8zto-4489770.xlsx")

db_vision <- list.files(pattern = "*-8nsp.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

library(readxl)

# db_vision <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-8nsp-4489770.xlsx")

db_mhealth <- list.files(pattern = "*-v2gn.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

library(readxl)
# db_mhealth <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-v2gn-4489770.xlsx")

@@

# bind (db_mhealth, db_vision, db_age, by = `Participant Private ID`)

colnames(db_age)
db_age$age_response_specific
db_age$gender_response
db_age$`gender_response-quantised`
# db_age$`AgeResponse-text`
db_age1<- select(db_age, c(1,13,16,35,36))

@@

library(readxl)
# db_IQ <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8/data_exp_60620-v2_task-esh8.xlsx")

@@

db_IQ1<- select(db_IQ, c(1,13,16, 37,40:44))

@@

colnames(db_IQ3)
db_IQ4<- select(db_IQ3,c(1,9,8))

@@

# left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS, by = "completion_code")

@@

db_BPQ3
# 
# left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3, by = "completion_code")

db_self_rep <- Reduce(merge, list(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS))

db_self_rep <- cbind(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS)

db_self_rep
write_csv(db_self_rep, "db_self_rep_345_356.csv")

write_csv(db_self_rep, "db_self_rep_350.csv")

@@

merge 
```{r}

db_self_rep
library(readr)
db_self_rep_350_1 <- read_csv("db_self_rep_350.1.csv")
# View(db_self_rep_350_1)

db_self_rep$`Event Index.x`<- NULL
db_self_rep$`Event Index.y`<-NULL
db_self_rep_350_1$`Event Index.y`<- NULL

db_self_rep_345_356<- bind_rows(db_self_rep,db_self_rep_350_1)
colnames(db_self_rep_345_356)

db_self_rep_345_356<- db_self_rep_345_356[,c(1:22)]

write_csv(db_self_rep, "db_self_rep_345_356_final.csv")
```
